\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-16 challenges.tex
phrasing

\revision{In this chapter, we discuss several problems that stand in the way of systematic exploration's applicability to kernel space. We address these problems in part with certain aspects of Landslide's design and in part by relying on the user to provide important information, which we discuss in Chapter~\ref{sec:design} and Chapter~\ref{sec:using} respectively.}

>>>>

\revision{In this chapter, we discuss several problems that stand in the way of systematic exploration's applicability to kernel space. We address these problems partly with certain aspects of Landslide's design and partly by relying on the user to provide important information, which we discuss in Chapter~\ref{sec:design} and Chapter~\ref{sec:using} respectively.}
